---
title: "Japanese General Elections"
#subtitle: "Exploratory Analysis"
author: "Populism in Regional Japan: Where is the 'Revenge of the Places That Don't Matter'?"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  rmdformats::readthedown:
    toc_depth: 3
---


```{r results='hide', echo=FALSE, include=FALSE}
p_needed <- c("tidyverse",
              "here",
              "cowplot",
              "readxl",
              "data.table",
              "magrittr",
              "rvest",
              "htmltab",
              "xml2",
              "gt",
              "lme4",
              "gtsummary",
              "gtExtras",
              "crosstable",
              "rmdformats",
              "ggcorrplot",
              "texreg",
              "plm",
              "sf",
              "spdep",
              "ggthemes",
              "ggpubr",
              "ggrepel",
              "ggsflabel",
              "ggspatial",
              "splm",
              "spatialreg",
              "viridis"
)
packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
lapply(p_needed, require, character.only = TRUE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
Elections <- read_csv(here("static", "htmlplots", "Data", "Elections2.csv"), col_names = TRUE)
```

```{r echo=FALSE}

# Elections <- Elections[,-c(5,8)]
Elections[, 5:7][Elections[, 5:7] == 0] <- NA

Elections2 <- Elections %>%
  filter(LDP>=0 | LDP %in% NA) %>%
  filter(LDP <=1 | LDP %in% NA) %>%
  filter(JCP>=0 | JCP %in% NA) %>%
  filter(JCP <=1 | JCP %in% NA)

Elections2$Year <- as.character(Elections2$Year)
Elections2$Year <- as.factor(Elections2$Year)

Elections2$Code <- as.character(Elections2$Code)
Elections2$Code <- as.factor(Elections2$Code)

Elections2 <- Elections2 %>%
  filter(!Code %in% NA) %>%
  mutate(Turnout = ifelse(Turnout >=1, NA, Turnout),
         EldPop = EldPop/100)

Elections3 <- Elections2[!duplicated(Elections2[,1:2]),]

Elections4 <- Elections3 %>%
  group_by(kuname) %>%
  filter(all(c("全部過疎", "Normal") %in% Kaso))

Elections5 <- Elections3 %>%
  group_by(kuname) %>%
  filter(all(c("全部過疎", "Normal", "一部過疎") %in% Kaso))

# https://stackoverflow.com/a/58207744
```


```{r include=FALSE}
Elections3 %>%
  group_by(Year) %>%
  summarise(n = n())
```


```{r include=FALSE}
# average municip per SMD

Elections3 %>%
#  filter(Year %in% 2021) %>%
  group_by(Year, kuname) %>%
  summarise(n = n()) %>%
  summarise(avgMun = mean(n))


# having both kaso and normal

Elections3 %>%
#  filter(Year %in% 2021) %>%
  group_by(Year, kuname) %>%
  filter(all(c('Normal','Kaso') %in% Kaso2)) %>%
  summarise(n = n()) %>%
  summarise(n = n())
```


```{r echo=FALSE}
my_pal <- scales::col_numeric(
  paletteer::paletteer_d(
    palette = "ggsci::red_material"
    ) %>% as.character(),
  domain = NULL
  )

```

# Exploratory tables

## Basic differences between "merged" and "non-merged"

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(!Year %in% 2009) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
  group_by(Year, Fusion) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Fusion") %>%
  fmt_number(
    columns = 2:13,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
  ) %>%
    data_color(
    columns = 2:13,
    colors = my_pal
    )
#   gtsave(
#     "merged.png"
# )
```

<br><br>

## Fiscal differences

### Merged / non-merged counts and proportions across kaso-types 

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE, include=FALSE}
Elections3 %>%
  select(Year, Fusion, Kaso) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
  tbl_summary(
    by = Year, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_overall() %>%
  modify_header(label = "**Variable**") %>% # update the column header
  bold_labels() 
```

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# Elections3 %>%
#   filter(Year %in% 2009,
#          Kaso %in% c("Normal", "みなし過疎", 
#                      "一部過疎", "全部過疎")) %>%
#   select(Year, Fusion, Kaso) %>%
#   mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
#                       labels = c("Non-Merged", "Merged"))) %>%
#   tbl_cross(
#     row = Fusion,
#     col = Kaso,
#     percent = "column",
#     label = list(Kaso ~ "2009", Fusion ~ "Fusion")
#   )

Elections3 %>%
  filter(Year %in% 2012) %>%
  select(Year, Fusion, Kaso) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
    mutate(Kaso = factor(Kaso, levels = c("Normal",
                                        "みなし過疎",
                                        "一部過疎",
                                        "全部過疎"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating"))) %>%
  tbl_cross(
    row = Fusion,
    col = Kaso,
    percent = "column",
    label = list(Kaso ~ "2012", Fusion ~ "Fusion")
  )

Elections3 %>%
  filter(Year %in% 2014) %>%
  select(Year, Fusion, Kaso) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
    mutate(Kaso = factor(Kaso, levels = c("Normal",
                                        "みなし過疎",
                                        "一部過疎",
                                        "全部過疎"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating"))) %>%
  tbl_cross(
    row = Fusion,
    col = Kaso,
    percent = "column",
    label = list(Kaso ~ "2014", Fusion ~ "Fusion")
  )

Elections3 %>%
  filter(Year %in% 2017) %>%
  select(Year, Fusion, Kaso) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
    mutate(Kaso = factor(Kaso, levels = c("Normal",
                                        "みなし過疎",
                                        "一部過疎",
                                        "全部過疎"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating"))) %>%
  tbl_cross(
    row = Fusion,
    col = Kaso,
    percent = "column",
    label = list(Kaso ~ "2017", Fusion ~ "Fusion")
  )

Elections3 %>%
  filter(Year %in% 2021) %>%
  select(Year, Fusion, Kaso) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
    mutate(Kaso = factor(Kaso, levels = c("Normal",
                                        "みなし過疎",
                                        "一部過疎",
                                        "全部過疎"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating"))) %>%
  tbl_cross(
    row = Fusion,
    col = Kaso,
    percent = "column",
    label = list(Kaso ~ "2021", Fusion ~ "Fusion")
  )
```

```{r include=FALSE}
# Elections3 %>%
#   select(Year, Fusion, Kaso) %>%
#   mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
#                       labels = c("Non-Merged", "Merged"))) %>%
#   crosstable(c(Fusion, Kaso), by=Year, total="both") %>%
#   as_flextable(keep_id=FALSE)
```



### Basic differences between "Normal" and "Kaso" 

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(Kaso2 %in% c("Kaso", "Normal"),
         !Year %in% 2009) %>%
  group_by(Year, Kaso2) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE), 
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso2") %>%
  fmt_number(
    columns = 2:13,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:13,
    colors = my_pal
    )
#   gtsave(
#     "kaso-nonkaso-unique.png"
# )
```


<!-- ### Basic differences between "Normal" and "Kaso" + Merged/Non-Merged -->

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE, include=FALSE}
Elections3 %>%
  group_by(Year, Kaso2.fusion) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                     `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                     `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                     `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                     `JCP-SMD` = mean(JCP, na.rm=TRUE),
                     `JCP-PR` = mean(JCPPR, na.rm=TRUE),
                     `JCP-Gap` = mean(JCPDif, na.rm=TRUE),
                     Turnout = mean(Turnout, na.rm=TRUE),
                     FStrength = mean(Fstrength, na.rm=TRUE),
                     LATperCapita = mean(LATperCapita, na.rm=TRUE), 
                     Elderly = mean(EldPop, na.rm=TRUE)
                     #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso2.fusion") %>%
  fmt_number(
    columns = 2:13,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(`JCP-SMD`, Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:13,
    colors = my_pal
    )
```


<br><br>

### Detailed differences (including types of "Kaso")

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(Kaso %in% c("Normal", "みなし過疎", 
                     "一部過疎", "全部過疎"),
         !Year %in% 2009) %>%
  mutate(Kaso = factor(Kaso, levels = c("Normal",
                                        "みなし過疎",
                                        "一部過疎",
                                        "全部過疎"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating"))) %>%
  group_by(Year, Kaso) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso") %>%
  fmt_number(
    columns = 2:13,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:13,
    colors = my_pal
    )
#   gtsave(
#     "kaso-detailed-unique.png"
# )
```



<br><br>

### Detailed differences (including types of "Kaso") + Merged/Non-Merged

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(Kaso.fusion %in% c("Normal", "みなし過疎", 
                     "一部過疎", "全部過疎", "全部過疎-Merged"),
         !Year %in% 2009) %>%
  mutate(Kaso.fusion = factor(Kaso.fusion, levels = c("Normal",
                                                           "みなし過疎",
                                                           "一部過疎",
                                                           "全部過疎",
                                                           "全部過疎-Merged"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating",
                                 "Fully depopulating (merged)"))) %>%
  group_by(Year, Kaso.fusion) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm = TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE),
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso.fusion") %>%
  fmt_number(
    columns = 2:13,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:13,
    colors = my_pal
    )
#   gtsave(
#     "kaso-merged-detailed-unique.png"
# )
```

<br><br>

## 2012 -- 2021 trends

## Basic differences between "merged" and "non-merged"

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(!Year %in% 2009) %>%
  mutate(Fusion = factor(Fusion, levels = c("0", "1"), 
                      labels = c("Non-Merged", "Merged"))) %>%
  group_by(Fusion) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Fusion") %>%
  fmt_number(
    columns = 2:12,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
  ) %>%
    data_color(
    columns = 2:12,
    colors = my_pal
    )
#   gtsave(
#     "merged.png"
# )
```


### Basic differences between "Normal" and "Kaso"

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(Kaso2 %in% c("Kaso", "Normal"),
         !Year %in% 2009) %>%
  group_by(Kaso2) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso2") %>%
  fmt_number(
    columns = 2:12,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:12,
    colors = my_pal
    )
#   gtsave(
#     "kaso-nonkaso-overall.png"
# )
```

### Detailed differences (including types of "Kaso") + Merged/Non-Merged

```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Elections3 %>%
  filter(Kaso.fusion %in% c("Normal", "みなし過疎", 
                     "一部過疎", "全部過疎", "全部過疎-Merged"),
         !Year %in% 2009) %>%
  mutate(Kaso.fusion = factor(Kaso.fusion, levels = c("Normal",
                                                           "みなし過疎",
                                                           "一部過疎",
                                                           "全部過疎",
                                                           "全部過疎-Merged"), 
                      labels = c("Normal", "Quasi-depopulating", 
                                 "Partly depopulating",
                                 "Fully depopulating",
                                 "Fully depopulating (merged)"))) %>%
  group_by(Kaso.fusion) %>%
  dplyr::summarize(`LDP-SMD` = mean(LDP, na.rm=TRUE),
                   `LDP-SMD-relative` = mean(LDP_relative, na.rm=TRUE),
                   `LDP-PR` = mean(LDPPR, na.rm=TRUE),
                   `LDP-PR-relative` = mean(LDPPR_relative, na.rm=TRUE),
                   `LDP-Gap` = mean(LDPDif, na.rm=TRUE),
                   `LDP-Gap-relative` = mean(LDPDif_relative, na.rm=TRUE),
                   Turnout = mean(Turnout, na.rm=TRUE),
                   `Turnout-relative` = mean(Turnout_relative, na.rm=TRUE),
                   FStrength = mean(Fstrength, na.rm=TRUE),
                   LATperCapita = mean(LATperCapita, na.rm=TRUE),
                   Elderly = mean(EldPop, na.rm=TRUE)
                   #SCapital = mean(social_capital, na.rm=TRUE)
                   ) %>%
  gt(rowname_col = "Kaso.fusion") %>%
  fmt_number(
    columns = 2:12,
    decimals = 3 # decrease decimal places
    ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = c(Turnout)
      ))) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Municipal characteristics**"),
    subtitle = md("*Aggregated by fiscal profiles*")
  ) %>%
    data_color(
    columns = 2:12,
    colors = my_pal
    )
#   gtsave(
#     "kaso-merged-detailed-overall.png"
# )
```


# Statistical analysis

```{r echo=FALSE}
# optionally exclude 2009

Elections3 <- Elections3 %>%
  filter(!Year %in% 2009)
```


## Summary statistics

```{r echo=FALSE, results='asis'}
Elections3[,-c(23:28)] %>%
  # Keep numeric variables
  select_if(is.numeric) %>%
  # gather variables
  gather(Variable, value) %>%
  # Summarize by variable
  group_by(Variable) %>%
  # summarise all columns
  summarise(n = sum(!is.na(value)),
            `Mean` = mean(value, na.rm = TRUE),
            `Std. Dev.` = sd(value, na.rm = TRUE),
            `Median` = median(value, na.rm = TRUE),
            `Min.` = min(value, na.rm = TRUE),
            `Max.` = max(value, na.rm = TRUE)) %>%
  gt() %>%
  fmt_number(
    columns = 3:7,
    decimals = 2) %>%
  fmt_number(
    rows = 4,
    columns = 3:7,
    decimals = 0) %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
    ) %>%
  tab_header(
    title = md("**Summary statistics**"))

```



## Correlation matrix

```{r echo=FALSE, results='asis'}
Elections3[,-c(6,11,13:15,18:20,22:30)] %>%
  select_if(is.numeric) %>%
  cor(use = "complete.obs") %>% 
  ggcorrplot(hc.order = TRUE, #hierarchical ordering
             type = "lower",
             lab = TRUE,
             lab_size = 4,
             outline.color = "white",
             colors = c("#6D9EC1", "white", "#E46726"),
             sig.level=0.05,
             insig = "blank") +
  theme(plot.background = element_rect(fill = "#303030", color = "#303030"),
        axis.text.x = element_text(colour = "grey", family = "serif", size = 15),
        axis.text.y = element_text(colour = "grey",family = "serif", size = 15),
        legend.title = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        plot.title = element_text(hjust = 0.5, color = "white", face="bold"))
```


## Regressions

### Turnout ratio

```{r echo=FALSE, include=FALSE}
TurnoutMod1 <- plm(Turnout ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

TurnoutMod2 <- plm(Turnout ~ Year + Fstrength + EldPop + LDP,
                   index=c("Code","Year"),
                   model = "pooling", data = Elections3)

TurnoutMod3 <- plm(Turnout ~ Year + Fstrength + EldPop + LDP + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(TurnoutMod3))
```


```{r echo=FALSE, include=FALSE}
TurnoutMod4 <- plm(Turnout_relative ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

TurnoutMod5 <- plm(Turnout_relative ~ Year + Fstrength + EldPop + LDP,
                   index=c("Code","Year"),
                   model = "pooling", data = Elections3)

TurnoutMod6 <- plm(Turnout_relative ~ Year + Fstrength + EldPop + LDP + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(TurnoutMod6))
```


```{r echo=FALSE, include=FALSE}
turnout.pooled <- plm(Turnout ~ Fstrength + LDP + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, model = "within", effect = "time")

turnout.fe <- plm(Turnout ~ Year + Fstrength + LDP + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, model = "within")

turnout.re <- plm(Turnout ~ Fstrength + LDP + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, 
                  model = "random")
```


#### Absolute values

```{r turnout, results='asis', echo=FALSE}
htmlreg(list(TurnoutMod1, TurnoutMod2, TurnoutMod3),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)",
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "LDP", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:Turnout"
       )
```


<br>

#### Values relative to SMD-average

```{r turnout2, results='asis', echo=FALSE}
htmlreg(list(TurnoutMod4, TurnoutMod5, TurnoutMod6),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)",
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "LDP", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:Turnout2"
       )
```

<br><br>

### LDP: SMD-Votes

```{r echo=FALSE, include=FALSE}
LDPMod1 <- plm(LDP ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPMod2 <- plm(LDP ~ Year + Fstrength + EldPop + Turnout, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPMod3 <- plm(LDP ~ Year + Fstrength + EldPop + Turnout + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(LDPMod6))
```

```{r echo=FALSE, include=FALSE}
LDPMod4 <- plm(LDP_relative ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPMod5 <- plm(LDP_relative ~ Year + Fstrength + EldPop + Turnout, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPMod6 <- plm(LDP_relative ~ Year + Fstrength + EldPop + Turnout + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(LDPMod6))
```


```{r echo=FALSE, include=FALSE}
ldp.pooled <- plm(LDP ~ Fstrength + Turnout + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, model = "within", effect = "time")

ldp.fe <- plm(LDP ~ Fstrength + Turnout + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, model = "within")

ldp.re <- plm(LDP ~ Fstrength + Turnout + Kaso.fusion + EldPop,
                  index=c("Code","Year"), data = Elections3, 
                  model = "random")
```


#### Absolute values

```{r ldp, results='asis', echo=FALSE}
htmlreg(list(LDPMod1, LDPMod2, LDPMod3),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)",
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "Turnout", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:LDP"
       )
```


<br>

#### Values relative to SMD-average

```{r ldp2, results='asis', echo=FALSE}
htmlreg(list(LDPMod4, LDPMod5, LDPMod6),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)", 
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "Turnout", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),Absolute
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:LDP2"
       )
```

<br><br>

### LDP: SMD-PR Difference

```{r echo=FALSE, include=FALSE}
LDPDifMod1 <- plm(LDPDif ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPDifMod2 <- plm(LDPDif ~ Year + Fstrength + EldPop + Turnout, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPDifMod3 <- plm(LDPDif ~ Year + Fstrength + EldPop + Turnout + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(LDPMod3))
```

```{r echo=FALSE, include=FALSE}
LDPDifMod4 <- plm(LDPDif_relative ~ Year + Fstrength, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPDifMod5 <- plm(LDPDif_relative ~ Year + Fstrength + EldPop + Turnout, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

LDPDifMod6 <- plm(LDPDif_relative ~ Year + Fstrength + EldPop + Turnout + 
                   Kaso.fusion, index=c("Code","Year"),
                   model = "pooling", data = Elections3)

#sqrt(car::vif(LDPMod3))
```


#### Absolute values

```{r ldpdif, results='asis', echo=FALSE}
htmlreg(list(LDPDifMod1, LDPDifMod2, LDPDifMod3),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)", 
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "Turnout", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:LDPDif"
       )
```


<br>

#### Values relative to SMD-average

```{r ldpdif2, results='asis', echo=FALSE}
htmlreg(list(LDPDifMod4, LDPDifMod5, LDPDifMod6),
       custom.model.names = c("Model 1", "Model 2", "Model 3"),
       custom.coef.names = c("(Intercept)",
                             "2014", "2017", "2021", "Fiscal Strength",
                             "Elderly", "Turnout", "みなし過疎",
                             "一部過疎", "全部過疎", "全部過疎-Merged"),
       groups = list("Year dummy (base group = '2012')" = 2:4,
         "Fiscal type (base group = 'Normal')" = 8:11),
       caption = NULL,
       digits = 2,
#       reorder.coef = c(2:8,1),
       include.ercomp = FALSE,
       single.row = FALSE,
       booktabs = TRUE,
       dcolumn = TRUE,
       caption.above = TRUE,
       threeparttable = TRUE,
       use.packages = FALSE,
       stars = c(0.01, 0.05, 0.1),
       label = "tab:LDPDif2"
       )
```


<br><br>

# Mapping

```{r include=FALSE}
projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

d3 <- sf::st_read("GIS/japan_ver81.shp") %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

d3 <- d3[,-c(3:5, 8:9)]
colnames(d3)[1] <- "Code"

Pref <- read.csv("GIS/JPref2.csv", stringsAsFactors = FALSE)
colnames(Pref)[1] <- "Code"

PrefMap <- sf::st_read("GIS/JPref.shp") %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

PrefMap2 <- as(PrefMap, "Spatial")

coord2 <- as.data.frame(coordinates(spTransform(PrefMap2, 
                                                CRS("+proj=longlat +datum=WGS84"))))
PrefCoord <- cbind(Pref, coord2)

senkyoku2017 <- rgdal::readOGR("GIS/senkyoku289/senkyoku289.shp", encoding = "shift-jis")
senkyoku2017 <- st_as_sf(senkyoku2017)
senkyoku2017$kucode <- sprintf("%05s", senkyoku2017$kucode)

senkyoku2017 <- senkyoku2017 %>%
  arrange(kucode)

senkyoku2017$ken <- as.numeric(senkyoku2017$ken)
senkyoku2017$ku <- as.numeric(senkyoku2017$ku)

senkyoku2014 <- rgdal::readOGR("GIS/senkyoku295/senkyoku295.shp", encoding = "shift-jis")
senkyoku2014 <- st_as_sf(senkyoku2014)
colnames(senkyoku2014)[1] <- "kucode"

senkyoku2014 <- senkyoku2014 %>%
  arrange(kucode)

senkyoku2014 <- senkyoku2014[-c(3:16)]


senkyoku1996 <- rgdal::readOGR("GIS/senkyoku300/senkyoku300.shp", encoding = "shift-jis")
senkyoku1996 <- st_as_sf(senkyoku1996)
colnames(senkyoku1996)[1] <- "kucode"

senkyoku1996 <- senkyoku1996 %>%
  arrange(kucode)

senkyoku1996 <- senkyoku1996[-c(3:16)]
```


```{r include=FALSE}
Elections3$PrefNumber <- Pref$Code[match(Elections3$Pref, Pref$Jpref)]

Elections3 <- Elections3 %>%
  separate(kuname, 
           into = c("EPref", "ku"), 
           sep = "(?<=[A-Za-z])(?=[0-9])"
           )


Elections4 <- merge(x = Elections3, y = d3[,c(1,5)], by = "Code", all.x = TRUE)
Elections4 <- st_as_sf(x = Elections4, crs = projcrs)
```

```{r include=FALSE}
Elections3 %>%
  filter(Year %in% 2021) %>%
  summarise(Turnout = quantile(Turnout, c(.1, .2, .3, .4, .5, .6, .7, .8, .9, 1), 
                               na.rm = TRUE))
```

```{r include=FALSE}
Elections3$ku <- as.numeric(Elections3$ku)

Elections2021 <- Elections3 %>%
  filter(Year %in% 2021) %>%
  mutate(District = paste0(EPref,ku)) 

Elections2021 <- Elections2021 %>%
  left_join(senkyoku2017[,c(3:5)], by = c("PrefNumber" = "ken",
                               "ku" = "ku"))

Elections2021 <- st_as_sf(x = Elections2021, crs = projcrs)


Elections2021Dist <- Elections3 %>%
  filter(Year %in% 2021) %>%
  mutate(District = paste0(EPref,ku)) %>% 
  distinct(District, .keep_all = TRUE) %>%
  left_join(senkyoku2017[,c(3:5)], by = c("PrefNumber" = "ken",
                               "ku" = "ku"))

Elections2021Dist <- st_as_sf(x = Elections2021Dist, crs = projcrs)
```


```{r include=FALSE}
align_legend <- function(p, hjust = 0.5)
{
  # extract legend
  g <- cowplot::plot_to_gtable(p)
  grobs <- g$grobs
  legend_index <- which(sapply(grobs, function(x) x$name) == "guide-box")
  legend <- grobs[[legend_index]]

  # extract guides table
  guides_index <- which(sapply(legend$grobs, function(x) x$name) == "layout")

  # there can be multiple guides within one legend box  
  for (gi in guides_index) {
    guides <- legend$grobs[[gi]]

    # add extra column for spacing
    # guides$width[5] is the extra spacing from the end of the legend text
    # to the end of the legend title. If we instead distribute it by `hjust:(1-hjust)` on
    # both sides, we get an aligned legend
    spacing <- guides$width[5]
    guides <- gtable::gtable_add_cols(guides, hjust*spacing, 1)
    guides$widths[6] <- (1-hjust)*spacing
    title_index <- guides$layout$name == "title"
    guides$layout$l[title_index] <- 2

    # reconstruct guides and write back
    legend$grobs[[gi]] <- guides
  }

  # reconstruct legend and write back
  g$grobs[[legend_index]] <- legend
  g
}
```


## Turnout

### 2021

```{r include=FALSE}
(mainland <- Elections4 %>%
   filter(Year %in% 2021) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile), colour = NA) +
   geom_sf(data = PrefMap,
           fill = NA,
           color = "black",
           size = 0.1) +
  coord_sf(xlim = c(128, 147), 
           ylim = c(30.1, 46),
           expand = FALSE) +
  scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10),
                     labels = c("53%", "57%", "61%",
                                "67%", "87%"),
                     name = "Voters' Turnout") +
  labs(title = "Turnout Ratio (2021)") +
  theme_map() +
  theme(axis.text=element_text(size=22),
        axis.text.x = element_text(vjust = 0.5, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title=element_text(size=24,face="bold"),
        legend.position = c(0.85, 0.5),
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5, size=25,face="bold"),
        legend.text=element_text(size=12),
        legend.title=element_text(size=13, face="bold"),
        legend.margin = margin(8, 8, 8, 8),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key = element_rect(fill = "white"),
        legend.box.background = element_rect(color="black", size=1),
        legend.key.width=unit(1.5, "cm"),
        legend.key.height = unit(1.5, "cm"))
)
```

```{r include=FALSE}
(Ryukyu <- Elections4 %>%
   filter(Year %in% 2021) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile),
           color = "black", size=0.1) +
  coord_sf(xlim = c(122.5, 130.5), 
           ylim = c(23.5, 30.1),
           expand = FALSE, datum = NA) +
  labs(title = NULL) +
   scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10)) +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  geom_text(data = PrefCoord %>%
                    filter(Code %in% c(47)),
                  aes(x = V1, y = V2, label = "Okinawa Pref.\n沖縄県"),
                  size = 10,
                  alpha = 0.5,
                  nudge_x = -1.5,
                  nudge_y = 1.5,
            family = "HiraKakuPro-W3"))
```

```{r echo=FALSE}
TurnoutRatio2021 <- mainland +
    annotation_custom(
      grob = ggplotGrob(Ryukyu),
      xmin = 129,
      xmax = 138,
      ymin = 36.5,
      ymax = 47.5
  ) +
  annotation_north_arrow(which_north = "grid", location = "br",  
                         height = unit(4, "cm"), width = unit(4, "cm"),
                         pad_x = unit(1, "cm"),
                         pad_y = unit(6, "cm")) +
  ggsn::scalebar(x.min = 128, x.max = 146.5,
                   y.min = 31, y.max = 46,
                   dist = 100, dist_unit = "km",
                   st.bottom = FALSE, st.color = "black",
             transform = TRUE, model = "WGS84")

ggdraw(align_legend(TurnoutRatio2021))
```


```{r}
# ggsave(filename = "Turnout2021.pdf", width = 15, height = 16, units = "in", device = cairo_pdf)
# ggsave(filename = "Turnout2021.png", width = 15, height = 16, units = "in")
```



### 2017

```{r include=FALSE}
(mainland <- Elections4 %>%
   filter(Year %in% 2017) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile), colour = NA) +
   geom_sf(data = PrefMap,
           fill = NA,
           color = "black",
           size = 0.1) +
  coord_sf(xlim = c(128, 147), 
           ylim = c(30.1, 46),
           expand = FALSE) +
  scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10),
                     labels = c("50%", "54%", "59%",
                                "65%", "97%"),
                     name = "Voters' Turnout") +
  labs(title = "Turnout Ratio (2017)") +
  theme_map() +
  theme(axis.text=element_text(size=22),
        axis.text.x = element_text(vjust = 0.5, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title=element_text(size=24,face="bold"),
        legend.position = c(0.85, 0.5),
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5, size=25,face="bold"),
        legend.text=element_text(size=12),
        legend.title=element_text(size=13, face="bold"),
        legend.margin = margin(8, 8, 8, 8),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key = element_rect(fill = "white"),
        legend.box.background = element_rect(color="black", size=1),
        legend.key.width=unit(1.5, "cm"),
        legend.key.height = unit(1.5, "cm"))
)
```

```{r include=FALSE}
(Ryukyu <- Elections4 %>%
   filter(Year %in% 2017) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile),
           color = "black", size=0.1) +
  coord_sf(xlim = c(122.5, 130.5), 
           ylim = c(23.5, 30.1),
           expand = FALSE, datum = NA) +
  labs(title = NULL) +
   scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10)) +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  geom_text(data = PrefCoord %>%
                    filter(Code %in% c(47)),
                  aes(x = V1, y = V2, label = "Okinawa Pref.\n沖縄県"),
                  size = 10,
                  alpha = 0.5,
                  nudge_x = -1.5,
                  nudge_y = 1.5,
            family = "HiraKakuPro-W3"))
```


```{r echo=FALSE}
TurnoutRatio2017 <- mainland +
    annotation_custom(
      grob = ggplotGrob(Ryukyu),
      xmin = 129,
      xmax = 138,
      ymin = 36.5,
      ymax = 47.5
  ) +
  annotation_north_arrow(which_north = "grid", location = "br",  
                         height = unit(4, "cm"), width = unit(4, "cm"),
                         pad_x = unit(1, "cm"),
                         pad_y = unit(6, "cm")) +
  ggsn::scalebar(x.min = 128, x.max = 146.5,
                   y.min = 31, y.max = 46,
                   dist = 100, dist_unit = "km",
                   st.bottom = FALSE, st.color = "black",
             transform = TRUE, model = "WGS84")

ggdraw(align_legend(TurnoutRatio2017))
```


```{r}
# ggsave(filename = "Turnout2017.pdf", width = 15, height = 16, units = "in", device = cairo_pdf)
# ggsave(filename = "Turnout2017.png", width = 15, height = 16, units = "in")
```


### 2014

```{r include=FALSE}
(mainland <- Elections4 %>%
   filter(Year %in% 2014) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile), colour = NA) +
   geom_sf(data = PrefMap,
           fill = NA,
           color = "black",
           size = 0.1) +
  coord_sf(xlim = c(128, 147), 
           ylim = c(30.1, 46),
           expand = FALSE) +
  scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10),
                     labels = c("47%", "51%", "56%",
                                "63%", "99%"),
                     name = "Voters' Turnout") +
  labs(title = "Turnout Ratio (2014)") +
  theme_map() +
  theme(axis.text=element_text(size=22),
        axis.text.x = element_text(vjust = 0.5, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title=element_text(size=24,face="bold"),
        legend.position = c(0.85, 0.5),
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5, size=25,face="bold"),
        legend.text=element_text(size=12),
        legend.title=element_text(size=13, face="bold"),
        legend.margin = margin(8, 8, 8, 8),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key = element_rect(fill = "white"),
        legend.box.background = element_rect(color="black", size=1),
        legend.key.width=unit(1.5, "cm"),
        legend.key.height = unit(1.5, "cm"))
)
```

```{r include=FALSE}
(Ryukyu <- Elections4 %>%
   filter(Year %in% 2014) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile),
           color = "black", size=0.1) +
  coord_sf(xlim = c(122.5, 130.5), 
           ylim = c(23.5, 30.1),
           expand = FALSE, datum = NA) +
  labs(title = NULL) +
   scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10)) +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  geom_text(data = PrefCoord %>%
                    filter(Code %in% c(47)),
                  aes(x = V1, y = V2, label = "Okinawa Pref.\n沖縄県"),
                  size = 10,
                  alpha = 0.5,
                  nudge_x = -1.5,
                  nudge_y = 1.5,
            family = "HiraKakuPro-W3"))
```

```{r echo=FALSE}
TurnoutRatio2014 <- mainland +
    annotation_custom(
      grob = ggplotGrob(Ryukyu),
      xmin = 129,
      xmax = 138,
      ymin = 36.5,
      ymax = 47.5
  ) +
  annotation_north_arrow(which_north = "grid", location = "br",  
                         height = unit(4, "cm"), width = unit(4, "cm"),
                         pad_x = unit(1, "cm"),
                         pad_y = unit(6, "cm")) +
  ggsn::scalebar(x.min = 128, x.max = 146.5,
                   y.min = 31, y.max = 46,
                   dist = 100, dist_unit = "km",
                   st.bottom = FALSE, st.color = "black",
             transform = TRUE, model = "WGS84")

ggdraw(align_legend(TurnoutRatio2014))
```


```{r}
# ggsave(filename = "Turnout2014.pdf", width = 15, height = 16, units = "in", device = cairo_pdf)
# ggsave(filename = "Turnout2014.png", width = 15, height = 16, units = "in")
```


### 2012

```{r include=FALSE}
(mainland <- Elections4 %>%
   filter(Year %in% 2012) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile), colour = NA) +
   geom_sf(data = PrefMap,
           fill = NA,
           color = "black",
           size = 0.1) +
  coord_sf(xlim = c(128, 147), 
           ylim = c(30.1, 46),
           expand = FALSE) +
  scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10),
                     labels = c("53%", "56%", "60%",
                                "65%", "87%"),
                     name = "Voters' Turnout") +
  labs(title = "Turnout Ratio (2012)") +
  theme_map() +
  theme(axis.text=element_text(size=22),
        axis.text.x = element_text(vjust = 0.5, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title=element_text(size=24,face="bold"),
        legend.position = c(0.85, 0.5),
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5, size=25,face="bold"),
        legend.text=element_text(size=12),
        legend.title=element_text(size=13, face="bold"),
        legend.margin = margin(8, 8, 8, 8),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key = element_rect(fill = "white"),
        legend.box.background = element_rect(color="black", size=1),
        legend.key.width=unit(1.5, "cm"),
        legend.key.height = unit(1.5, "cm"))
)
```

```{r include=FALSE}
(Ryukyu <- Elections4 %>%
   filter(Year %in% 2012) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile),
           color = "black", size=0.1) +
  coord_sf(xlim = c(122.5, 130.5), 
           ylim = c(23.5, 30.1),
           expand = FALSE, datum = NA) +
  labs(title = NULL) +
   scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10)) +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  geom_text(data = PrefCoord %>%
                    filter(Code %in% c(47)),
                  aes(x = V1, y = V2, label = "Okinawa Pref.\n沖縄県"),
                  size = 10,
                  alpha = 0.5,
                  nudge_x = -1.5,
                  nudge_y = 1.5,
            family = "HiraKakuPro-W3"))
```

```{r echo=FALSE}
TurnoutRatio2012 <- mainland +
    annotation_custom(
      grob = ggplotGrob(Ryukyu),
      xmin = 129,
      xmax = 138,
      ymin = 36.5,
      ymax = 47.5
  ) +
  annotation_north_arrow(which_north = "grid", location = "br",  
                         height = unit(4, "cm"), width = unit(4, "cm"),
                         pad_x = unit(1, "cm"),
                         pad_y = unit(6, "cm")) +
  ggsn::scalebar(x.min = 128, x.max = 146.5,
                   y.min = 31, y.max = 46,
                   dist = 100, dist_unit = "km",
                   st.bottom = FALSE, st.color = "black",
             transform = TRUE, model = "WGS84")

ggdraw(align_legend(TurnoutRatio2012))
```


```{r}
# ggsave(filename = "Turnout2012.pdf", width = 15, height = 16, units = "in", device = cairo_pdf)
# ggsave(filename = "Turnout2012.png", width = 15, height = 16, units = "in")
```


```{r}
# p <- plot_grid(TurnoutRatio2012, TurnoutRatio2014, 
#                TurnoutRatio2017, TurnoutRatio2021,
#                labels = "AUTO")
# 
# ggsave(filename = "Turnout.pdf", p, device = cairo_pdf)
```



## Nagano 2021

```{r include=FALSE}
Nagano2021 <- Elections4 %>%
  filter(Year %in% 2021,
         EPref %in% "Nagano",
         ku == 4)
```


```{r echo=FALSE}
Elections4 %>%
   filter(Year %in% 2021) %>%
   mutate(TurnoutDecile = dplyr::ntile(Turnout, 10)) %>%
   filter(EPref %in% "Nagano") %>%
   ggplot() +
   geom_sf(aes(fill = TurnoutDecile), colour = NA) +
   geom_sf(data = Elections2021Dist %>%
             filter(EPref %in% "Nagano"),
           fill = NA,
           color = "white",
           size = 1.5) +
  scale_fill_viridis(option="F", direction = -1,
                     breaks = c(2, 4, 6, 8, 10),
                     labels = c("53%", "57%", "61%",
                                "67%", "87%"),
                     name = "Voters' Turnout") +
  scale_x_continuous(breaks = seq(137.4, 138.8, by = .4)) +
  geom_sf_label_repel(data = Nagano2021 %>%
                        filter(Kaso2 %in% "Normal"),
                  aes(label = Kaso2),
                  fontface = 'bold',
                  color = 'black',
                  size = 5,
                  box.padding = unit(0.35, "lines"),
                  point.padding = unit(0.5, "lines"),
                  fill="springgreen4",
                  segment.color = 'black',
                  alpha = 0.8,
                  fun.geometry = sf::st_centroid) +
  geom_sf_label_repel(data = Nagano2021 %>%
                        filter(Kaso2 %in% "Kaso"),
                  aes(label = Kaso2),
                  fontface = 'bold',
                  color = 'white',
                  size = 5,
                  box.padding = unit(0.35, "lines"),
                  point.padding = unit(0.5, "lines"),
                  fill="red4",
                  segment.color = 'black',
                  alpha = 0.8,
                  fun.geometry = sf::st_centroid) +
  geom_sf_label_repel(data = Elections2021Dist %>%
                        filter(EPref %in% "Nagano"),
                  aes(label = ku),
                  fontface = 'bold',
                  color = 'black',
                  size = 15,
                  box.padding = unit(0.35, "lines"),
                  point.padding = unit(0.5, "lines"),
                  segment.color = 'black',
                  alpha = 0.8,
                  fun.geometry = sf::st_centroid) +
  labs(title = "Turnout Ratio, Nagano-ken (2021)") +
  theme_map() +
  theme(axis.text=element_text(size=22),
        axis.text.x = element_text(vjust = 0.5, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title=element_text(size=24,face="bold"),
        legend.position = c(0.7, 0.1),
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5, size=25,face="bold"),
        legend.text=element_text(size=12),
        legend.title=element_text(size=13, face="bold"),
        legend.margin = margin(8, 8, 8, 8),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key = element_rect(fill = "white"),
        legend.box.background = element_rect(color="black", size=1),
        legend.key.width=unit(1.5, "cm"),
        legend.key.height = unit(1.5, "cm"))
```

```{r}
# ggsave(filename = "NaganoTurnout2021.pdf", width = 15, height = 16, units = "in", device = cairo_pdf)
# ggsave(filename = "NaganoTurnout2021.png", width = 15, height = 16, units = "in")
```